\documentclass[a4paper,10pt]{article}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[margin=0.7in]{geometry}
\usepackage{texlogos}% provides the C++ logo as \cpluspluslogo
\usepackage{import}
\usepackage{hyperref}

%References
\import{reference-styles/}{cv.tex}
\ExecuteBibliographyOptions{doi=true}
\addbibresource{bibliography/references.bib}

\hypersetup{colorlinks=true,urlcolor=blue}

\setlength{\parindent}{0em}
\setlength{\parskip}{1ex}

\setlist{noitemsep}

\pagestyle{myheadings}
\markright{Christopher Brown} %Add my name in the header

\begin{document}
\begin{center}
\Large{Christopher Brown\\
\vskip 0.5ex
Curriculum Vitae}
\vskip 1ex
\hrule
\end{center}

\subsubsection*{Personal Details}
\begin{tabbing}
\hspace{8em} \= \kill
Address \> \input{address}\\
Telephone \> \input{telephone}\\
Email \> \href{mailto:pyrrhicpachyderm@gmail.com}{pyrrhicpachyderm@gmail.com}\\
Visa Status \> New Zealand \& British Citizen\\
ORCID \> 0000-0002-0393-3477
\end{tabbing}
\hrule

\subsubsection*{Profile}
I am a self motivated, high achieving student, with a sharp attention to detail.
I am currently pursuing my PhD as a member of the ALJE Lab at the University of Queensland, studying antibiotic resistance through the lens of competition theory.
I attained my Master's degree in Ecology as a member of the Stouffer Lab at the University of Canterbury, achieving A+ level throughout.
I completed my undergraduate degree at the University of Canterbury reading for a triple major in Mathematics, Biology and Computer Science.
I completed 495 points across 31 courses, all at A+ level.

I have represented New Zealand three times at the International Olympiad in Informatics (algorithmic design and implementation).
I graduated from Christ's College, Canterbury as Proxime Accessit, achieving Excellence at NCEA Level 3 with Excellence endorsements in Calculus, Statistics, Biology, Chemistry and Physics.
\vskip 2ex
\hrule

\subsubsection*{Employment \& Research Experience}
\textbf{February 2024 -- present:} Demonstrating in labs for 200 level Biostatistics at the University of Queensland, in Semester 1 each year.

\textbf{February 2019 -- November 2022:} Demonstrating in labs and running tutorials for several courses at the University of Canterbury.
\begin{itemize}[topsep=0em] %topsep sets space between above paragraph and list
	\item 2019--2022 Semester 1: 200 level Biological Data Analysis
	\item 2020--2022 Semester 2: 300 level Biological Data Analysis
	\item 2021 \& 2022 Semester 1: 300 level Global Change and Biosecurity
	\item 2019 Semester 2: 100 level Discrete Mathematics
	\item 2019 Semester 2: 200 \& 400 level Data Wrangling
\end{itemize}

\textbf{November 2018 -- February 2019 \& November 2019 -- February 2020:}
Completed two Summer Research Scholarships in the Stouffer Lab at the University of Canterbury.
I extensively modified a piece of network alignment software and applied it to food webs and metabolic networks.
I also wrote software to perform agent-based modelling of species competition.
I am currently writing these projects into papers for publication, as an ongoing project.

\textbf{December 2017 -- November 2018:}
Part-time work at QuickSense Education, writing practice questions and explanations for NCEA Level 1--3 students in Mathematics, Biology, Physics and Statistics.

\textbf{2014 Easter school break:}
Worked for Cyclone Computers to upgrade the computers for professors and other staff members at Lincoln University.

\vskip 2ex
\hrule

\subsubsection*{Education}
\begin{itemize}
\setlength{\itemsep}{0.2ex}
\item I am pursuing an PhD as part of the ALJE Lab at the University of Queensland.
\item I have completed an MSc in Ecology as part of the Stouffer Lab at the University of Canterbury, maintaining the maximum GPA of 9.
\item I have completed a BSc at the University of Canterbury, majoring in Mathematics, Biology and Computer Science, and maintaining the maximum GPA of 9. This includes first year university Mathematics and Computer Science STAR courses taken in Years 12 and 13.
\item I have achieved the following:\begin{itemize}
\item NCEA Levels 1, 2 and 3 with Excellence.
\item NCEA Excellence endorsements at Levels 1, 2 and 3 for Biology, Chemistry and Physics.
\item NCEA Excellence endorsements in Mathematics at Level 2 in Year 9 (2012), in Statistics at Level 3 in Year 10 (2013) and in Calculus at Level 3 in Year 11 (2014).
\item NZQA Scholarship in Statistics in Years 10, 12 and 13, Scholarship in Calculus in Years 11, 12 and 13 (with Outstanding in Year 12), and Scholarships in Chemistry and Physics in Year 13 (with Outstanding in Physics).%Line break before 12
\end{itemize}
\end{itemize}
%\hrule
\newpage

\subsubsection*{Achievements}
\begin{itemize}
\item Awarded a UQ scholarship for PhD tuition costs and living stipend (2024--present).
\item Awarded a UC Master's Scholarship (2022--2023).
\item Awarded a UC College of Engineering Mathematics and Statistics STAR Scholarship (2017--2019).
\item Awarded a UC Senior Scholarship, a Page Memorial Prize (for Mathematics) and a Percival Memorial Prize (for Biology) in 2019.
\item Selected to represent New Zealand at the International Olympiad in Informatics in Years 11, 12 and 13, achieving a bronze medal in 2015. 
\item Co-authored four Mathematics papers published in UK journals aimed at high achieving secondary school and University students.
\item Placed first in the University of Otago Junior Mathematics Competition in Years 9 and 11, and placed second in Year 10.
\end{itemize}
\hrule

\subsubsection*{Skills}
\begin{itemize}
\item Programming
\begin{itemize}
\item Extensive experience with C and \cpluspluslogo.
\item Completed courses on parallelising C using OpenMP and MPI.
\item Completed and tutored courses on R, in addition to using it for many other projects, and writing a package for it (\texttt{rescomp}).
\item Completed several University courses using Python.
\item Contributed extensively to an open source project using Lua.
\item Bash, including scripts for data format conversion and data trawling from online databases.
\item Extensive experience with Make (a build automation tool).
\item Algorithmic design, implementation, and debugging in a time-limited, competitive environment (informatics).
\end{itemize}
\item Document preparation
\begin{itemize}
\item Extensive experience in typesetting using LaTeX, including documents with equations and figures, and TikZ and PGFPlots for diagrams and graphs.
\item Referencing using BibLaTeX, including extensive customisation of referencing styles.
\end{itemize}
\item Statistical analysis, including tutoring courses on classical statistics, and experience with Bayesian model fitting.
\item Using Git for collaborative version control of C, R, and LaTeX projects.
\item Excellent problem solving skills, as evidenced by my achievements.
\item Experience writing research papers, and submitting them for publication.
\item Data wrangling, including teaching a course on the topic.
\end{itemize}


\vskip 2ex
\hrule

\subsubsection*{Research Outputs}

\fullcite{cervantes2023environmental}

\fullcite{bolourchi2025evolution}

\fullcite{brown2025simplifying}

\end{document}
